The starting grid in Formula 1: 2025

### 2025-12-11 inst/grid.Rmd
likelihood function plot for F1

```{r calcpoll, cache=TRUE}
jj <- f1grid(0.5)
```

```{r maxcalc, cache=TRUE}
mH <- maxp(jj)
```

```{r}
mH
```

>>>>

```{r calcpoll, cache=TRUE}
supptime  <- system.time(jj <- f1grid(0.5))
```

```{r maxcalc, cache=TRUE}
maxtime <- system.time(mH <- maxp(jj))
```

```{r}
supptime
maxtime
mH
pie(mH)
```

```{r domore, cache=TRUE}
o <- function(lambda){maxp(f1grid(lambda), give=TRUE)$value}
timeo1 <- system.time(l1 <- o(1.01))
timeo2 <- system.time(l2 <- o(1.02))
```

```{r}
timeo1
timeo2
l1
l2
```

```{r domanyL, cache=TRUE}
lam <- seq(from=0.9, to=1, len=17)
L <- sapply(lam, o)
```

```{r plotmanyL}
plot(lam, L - max(L), pch=16, type="b")
```
